---
title: "glmAnova.Rmd"
author: "Erika"
date: "5/5/2020"
output: html_document
---
```{r}
rm(list = ls())
library(MASS)
library(caret)
library(dplyr)
library(ggplot2)
```
Load the draft data
```{r}
KA<-read.csv("Covariates.csv")

#LS<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/2019-2020/Leslie/SYEvariables.csv")
```
Deal with NA's.

Stepwise regression won't work well if you have different amounts of data for the different regression runs.  Thus, we need a data set with the same data for each regression model. In Kate's data, there are some cameras for which there were no species detected.  We will delete them from the data set.
```{r}
dump<-which(is.na(KA$SpecRichness))
KA<-KA[-dump,]
```

Isolate response and predictor variables
```{r}
Kresponse<-KA[, c(7: 8, 18:19)]
Kpreds<- KA[, c(4, 6, 9:17, 21:57)]
Kpreds<- dplyr::select(Kpreds, -starts_with("P_Barren"))
Kpreds<-dplyr:: select(Kpreds, -starts_with("PlotShape"))

```
Now if there are any predictors remaining for which there are NA's, we should remove them from the predictor list. Use dplyr to find them.

```{r}
haveNAs<-Kpreds %>% select_if(function(x) any(is.na(x))) %>% names()
#returns column names that contain NAs
```
Now remove those columns from Kpreds
```{r}
Kpreds<-dplyr::select(Kpreds, - all_of(haveNAs))
```

Now let's run a stepwise regression

Set seed for reproducibility
```{r}
set.seed(123)
```
Let's run a two-way glm ANVOA to compare mean SR between forest type and season.

```{r}
#Species Richness
m.two_way<-glm(SpecRichness ~ ForestType * Season, data = KA)
summary(m.two_way)

#Shannon Diversity
SH.two_way<-glm(div_shan ~ ForestType * Season, data = KA)
summary(SH.two_way)

#Inverse Simpson's Diversity
S.two_way<-glm(inv_simp ~ ForestType * Season, data = KA)
summary(S.two_way)
```
Use aov 
```{r}
#Species Richness
m.aov<-aov(SpecRichness ~ ForestType * Season, data = KA)
summary(m.aov)

#Shannon Diversity
SH.aov<-aov(div_shan ~ ForestType * Season, data = KA)
summary(SH.aov)

#Inverse Simpson's Diversity
S.aov<-aov(inv_simp ~ ForestType * Season, data = KA)
summary(S.aov)
```
Because the interaction term was non-significant, run model again as 2-way with no interaction term.

```{r}
#Species Richness
m.aov1<-aov(SpecRichness ~ ForestType + Season, data = KA)
summary(m.aov1)

#Shannon Diversity
SH.aov1<-aov(div_shan ~ ForestType + Season, data = KA)
summary(SH.aov1)

#Inverse Simpson's Diversity
S.aov1<-aov(inv_simp ~ ForestType + Season, data = KA)
summary(S.aov1)
```
Now do tukey test to see which seasons are sig dif

```{r}
#Species Richness
TukeyHSD(m.aov1)

#Shannon Diversity
TukeyHSD(SH.aov1)

#Inverse Simpson's Diversity
TukeyHSD(S.aov1)
```
Get means for plots
```{r}
#Species Richness
mymeans<-KA %>% group_by(ForestType, Season) %>% summarize(
  meanSR= mean(SpecRichness, na.rm = T),
  sdSR = sd(SpecRichness, na.rm = T), 
  N= length(SpecRichness)
)
mymeans1<-KA %>% group_by(ForestType) %>% summarize(
  meanSR= mean(SpecRichness, na.rm = T),
  sdSR = sd(SpecRichness, na.rm = T), 
  N= length(SpecRichness)
)


#Shannon Diveristy
mymeansShan<-KA %>% group_by(ForestType, Season) %>% summarize(
  meanShan= mean(div_shan, na.rm = T),
  sdShan = sd(div_shan, na.rm = T)
)

meandecidpineShan<-KA %>% group_by(ForestType) %>% summarize(
  meanSimp= mean(div_shan, na.rm = T),
  sdSR = sd(div_shan, na.rm = T), 
  N= length(div_shan)
)

#Inverse Simpson's Diversity
mymeansSimp<-KA %>% group_by(ForestType, Season) %>% summarize(
  meanSimp= mean(inv_simp, na.rm = T),
  sdSimp = sd(inv_simp, na.rm = T)
)

meandecidpineSimp<- KA %>% group_by(ForestType) %>% summarise(
  meanSimp = mean(inv_simp, na.rm = T),
  sdSimp = sd(inv_simp, na.rm = T),
  N = length(div_shan)
)
```
Now plot:
```{r}
#Species Richness
dodge <- position_dodge(width = 0.9)

ggplot(mymeans, aes(ForestType, meanSR, group = Season, fill = Season))+
  geom_col(position = dodge)+ xlab("Forest Type") + ylab("Mean Species Richness")+
  geom_errorbar(aes(ymin = meanSR - sdSR, ymax = meanSR+sdSR), position = dodge, width = 0.25)

ggsave("SigMeanSR.jpg", device = "jpg")

#Shannon Diversity
dodge <- position_dodge(width = 0.9)

Shan<-ggplot(mymeansShan, aes(ForestType, meanShan, group = Season, fill = Season))+
  geom_col(position = dodge)+ xlab("Forest Type") + ylab("Mean Shannon Diversity")+
  geom_errorbar(aes(ymin = meanShan - sdShan, ymax = meanShan+sdShan), position = dodge, width = 0.25)
Shan<- Shan + coord_cartesian(ylim = c(0,5))

ggsave("SigMeanShan.jpg", device = "jpg")

#Inverse Simpson's Diversity
dodge <- position_dodge(width = 0.9)

Simp<- ggplot(mymeansSimp, aes(ForestType, meanSimp, group = Season, fill = Season))+
  geom_col(position = dodge)+ xlab("Forest Type") + ylab("Mean Simpson's Diversity")+
  geom_errorbar(aes(ymin = meanSimp - sdSimp, ymax = meanSimp+sdSimp), position = dodge, width = 0.25)
Simp<- Simp + coord_cartesian(ylim = c(0,5))

ggsave("SigMeanSimp.jpg", device = "jpg")

library(ggpubr)
SimpShan<-ggarrange(Simp,Shan, ncol = 2, nrow = 1, legend = "right", common.legend = TRUE)
SimpShan

ggsave("SimpShanSigMean.jpg", device = "jpg")
```
Another way to plot (that might be more informative) is whisker plots
```{r}
ggplot(mymeans, aes(ForestType, meanSR, group = Season, fill = Season))+
  geom_boxplot(position = dodge)+
  geom_point(position = dodge)
```

