---
title: "Cleaning Data"
output: html_notebook
---

The purpose of this R markdown is to clean the data produced from "checkTheseList.Rmd" to prepare it for calculating species accumulation curve, species richness, diversity, and other measurements. 

```{r}
rm(list = ls())
library(dplyr)
library(magrittr)
library(stringr)
library(tidyr)
library(ggplot2)

library(readr)
DF <- read_csv("~/Dropbox/Zooniverse_work/files for kate/Zooniverse-work-final/Zoo-Data-Wrangling/Data/north-country-wild-classifications.03.16.20-flattened.csv")


#all_data <- read_csv("~/Documents/Kate_ThesisCode/Good_Votes.csv") #This includes only the classifications we are certain about
#all_data<- read_csv("~/Documents/Kate_ThesisCode/cleaned_data.csv") #This is the data frame for all of the classifications including the ones we need to classify ourselves. 
all_data<- read_csv("~/Documents/Kate_ThesisCode/all_data.csv") #This is the df for all corrected classifications, including ones we corrected manually.

```


Match the forest type with subject ID
```{r}
Sifted_data<- DF[match(unique(DF$subject_ids), DF$subject_ids),]

#write.csv(Sifted_data, file = "Sifted_data.csv")
```

The final data frame did not contain dates. We need to add these in. 
```{r}
Metadata <- read.csv("~/Dropbox/Zooniverse_work/Game Camera Metadata Field Sheets 2019.csv")

Metadata1<- select(Metadata, Date.Out, Date.Checked, SD.Card.Number, Unit.Number, Round.Number) 

names(Metadata1)<- c("Date_Out", "Date_Checked", "SDCard", "Camera", "Round.Number")

```



Import final dataset to add dates column. We need to add date in the field and date retrieved in order to calculate species accumulation curve. 
```{r}
#You must keep round in the DF because otherwise the dates will not carry over. R cannot tell which dates go to which subjects without the round number specified. 
Sifted_data1<-select(Sifted_data, "subject_ids", "Imj1", "Imj2", "Img3", "CamNum", "SD_card_num", "ForestType", "ForestName", "round", "batch")

Sifted_data1<-arrange(Sifted_data1, desc(subject_ids))
all_data<-arrange(all_data, desc(subject_ids))

Sifted_data1<-Sifted_data1[order(Sifted_data1$subject_ids),]
all_data<-all_data[order(all_data$subject_ids),]

joinedData<- merge(all_data, Sifted_data1, by = 'subject_ids')
#Diff_species column is not quite right, but everything else appears to be correct.


#Be sure the merging columns have the same names and are both characters

#Data_Clean_up$CamNum<- as.character(Data_Clean_up$CamNum)
#Data_Clean_up$SD_card_num<- as.character(Data_Clean_up$SD_card_num)
joinedData$CamNum<- as.character(joinedData$CamNum)
joinedData$SD_card_num<- as.character(joinedData$SD_card_num)
joinedData$round<-as.character(joinedData$round)

Metadata1$Camera<-as.character(Metadata1$Camera)
Metadata1$SDCard<-as.character(Metadata1$SDCard)
Metadata1$Round.Number<-as.character(Metadata1$Round.Number)


joinFinal <- left_join(joinedData, Metadata1, by=c("round"="Round.Number", "CamNum"="Camera","SD_card_num"="SDCard"), type='right', match='all') 


write.csv(joinFinal, file = "joinedData.csv")
```

This seemed to match the correct deployment and collection date for each subject_id. Now we can do a species accumulation curve. 

NOTE: Need to be sure that all round numbers are filled in. Otherwise, NAs will appear in the dates and you will need to manually fix them.

