---
title: "Shannon and Simpson’s indices"
author: "Erika and Kate"
date: "4/25/2019"
output: html_document
---
We'd like to calculate the Shannon, Simpon, and inverse Simpson indices for the 2018-2020 camera trap data. We will be calculating the diversity per camera per season and per forest (the average diversity of the cameras in the forest across all seasons). 

Simpson's Index (D) measures the probability that two individuals randomly selected from a sample will belong to the same species. 

Inverse Simpson's Index measures true diversity from the Simpson's Index.

Shannon Index is a typical diversity index that accounts for species richness and evenness.

Set up workspace
```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(ggpubr)
library(readr)
```

Now load "raw" camera trap data
```{r}
DF<- read_csv("~/Documents/Kate_ThesisCode/dataFinal.csv")

```
Now get rid of the "NOTHINGHERE" and "SOMETHINGHERE" and other species that are not mammals since they provide no species information.

```{r}
dump<-which(DF$choice == "NOTHINGHERE" | DF$choice == "SOMETHINGHERE" | DF$choice == "HUMAN" | DF$choice == "GROUSERUFFED" | DF$choice == "CROWORRAVEN" | DF$choice == "OTHERBIRD" | DF$choice == "DOMESTICDOG" | DF$choice == "OWL" | DF$choice == "BLUEJAY" | DF$choice == "TURKEY" | DF$choice == "GOOSEWILD")

#now dump
DF<-DF[-dump,]
```

Next, we need to create a matrix or df of sites on rows and species on columns with cells equal to # of events.

Summarize by species and forest and return # of events.

```{r}
diversity<-DF %>% group_by(ForestName, choice) %>% summarise(
	NumEvents = length(CamNum)
)
```
Now we need to format diversity for vegan.

Use tidyr
```{r}
library(tidyr)
divVegan<- spread(diversity, choice, NumEvents)
```

Now, for vegan, replace NA's with zero and also delete the first column.

```{r}
#replace NAs with zeros
divVegan[is.na(divVegan)] <- 0
#dump first column
vegReady<-divVegan[,-1]
```

Run the diversity function for shannon diveristy index (increases as diversity increases)
```{r}
div_shan<-diversity(vegReady, index = "shannon")
div_shan
```

Do the same for the simpson's index (similarity index- take 1-S to find diversity index). Measurement of probability that any two randomly selected individuals from infinitely large community will belong to same species.
```{r}
div_simp<- diversity(vegReady, index = "simpson")
div_simp

inv_simp<- diversity(vegReady, index = "invsimpson")
```

Plot the two indices, bar graph of all forest sites. Box plot for two forest types. 

Create DF with forest name in one column and diversity in another. 
```{r}
library(tidyr)
Forest<- unique(divVegan$ForestName)
shanDiv<- as.data.frame(cbind(div_shan, Forest))

```

Plot bar graph of Shannon Index Diversity
```{r}
shanDiv$Type<- as.factor(c("D","P","D","D","P","P"))
shanDiv$div_shan<- as.numeric(as.character(shanDiv$div_shan))
ggplot(shanDiv, aes(x= Forest, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Forest") +
     ylab("Shannon Diversity Index")
     

ggsave("Shannon_Diversity_Index.jpg", device= "jpg")
write.csv(shanDiv, file = "shanDiv.csv")
```

Do the same for Simpson's Index
```{r}
simpDiv<-as.data.frame(cbind(div_simp, Forest))
simpDiv$Type<- as.factor(c("D","P","D","D","P","P"))

simpDiv$div_simp<- as.numeric(as.character(simpDiv$div_simp))
ggplot(simpDiv, aes(x= Forest, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index.jpg", device = "jpg")
write.csv(simpDiv, file = "simpDiv.csv")
```

Inverse Simpson's Index
```{r}
invSimp<-as.data.frame(cbind(inv_simp, Forest))
invSimp$Type<- as.factor(c("D","P","D","D","P","P"))

invSimp$inv_simp<- as.numeric(as.character(invSimp$inv_simp))
ggplot(invSimp, aes(x= Forest, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index.jpg", device = "jpg")
write.csv(invSimp, file = "invSimp.csv")
```

Join all data frames together to get one big one to summarise. 
```{r}
Forest_Div_Overall<-left_join(invSimp, shanDiv, "Forest")
Forest_Div_Overall<- left_join(Forest_Div_Overall, simpDiv, "Forest")
```



Calculations to find the standard deviation and mean for diversity indices in deciduous and pine study sites. 
```{r}
target <- c("SH", "BC", "DON")
Deciduous<- filter(Forest_Div_Overall, Forest %in% target)


MeanDecidDiv<- Deciduous %>% summarise(
     meaninvSimp = mean(inv_simp),
     sdinvSimp = sd(inv_simp),
     meansimp = mean(div_simp),
     sdsimp= sd(div_simp),
     meanshan = mean(div_shan),
     sdshan= sd(div_shan)
)

pines <- c("DEG", "WF", "WHIP")
Pines<- filter(Forest_Div_Overall, Forest %in% pines)


MeanPineDiv<- Pines %>% summarise(
      meaninvSimp = mean(inv_simp),
     sdinvSimp = sd(inv_simp),
     meansimp = mean(div_simp),
     sdsimp= sd(div_simp),
     meanshan = mean(div_shan),
     sdshan= sd(div_shan)
)
```

Now that we have identified the diversity per forest (average of cameras in forests across all seasons), we can identify the diversity per camera per season and diversity per forest per season.
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)
DF<- read_csv("~/Documents/Kate_ThesisCode/dataFinal.csv")

dump<-which(DF$choice == "NOTHINGHERE" | DF$choice == "SOMETHINGHERE" | DF$choice == "HUMAN" | DF$choice == "GROUSERUFFED" | DF$choice == "CROWORRAVEN" | DF$choice == "OTHERBIRD" | DF$choice == "DOMESTICDOG" | DF$choice == "OWL" | DF$choice == "BLUEJAY" | DF$choice == "TURKEY" | DF$choice == "GOOSEWILD")

#now dump
DF<-DF[-dump,]
```

The first step is to subset the data frame to make individual data frames per round. We will use these data frames to define diversity per forest and per camera.
```{r}
Round1<-filter(DF, round==1)
Round2<- filter(DF, round==2)
Round3<- filter(DF, round==3)
Round4<- filter(DF, round==4)
```

Calculate diversity per forest per season 
```{r}
diversityR1<-Round1 %>% group_by(ForestName, choice) %>% summarise(
	NumEvents = length(CamNum)
)
diversityR2<-Round2 %>% group_by(ForestName, choice) %>% summarise(
	NumEvents = length(CamNum)
)
diversityR3<-Round3 %>% group_by(ForestName, choice) %>% summarise(
	NumEvents = length(CamNum)
)
diversityR4<-Round4 %>% group_by(ForestName, choice) %>% summarise(
	NumEvents = length(CamNum)
)

library(tidyr)
divVeganR1<- spread(diversityR1, choice, NumEvents)
divVeganR2<- spread(diversityR2, choice, NumEvents)
divVeganR3<- spread(diversityR3, choice, NumEvents)
divVeganR4<- spread(diversityR4, choice, NumEvents)
```

Now, for vegan, replace NA's with zero and also delete the first column.
```{r}
#replace NAs with zeros
divVeganR1[is.na(divVeganR1)] <- 0
divVeganR2[is.na(divVeganR2)] <- 0
divVeganR3[is.na(divVeganR3)] <- 0
divVeganR4[is.na(divVeganR4)] <- 0

#dump first column
vegReadyR1<-divVeganR1[,-1]
vegReadyR2<-divVeganR2[,-1]
vegReadyR3<-divVeganR3[,-1]
vegReadyR4<-divVeganR4[,-1]
```

Run the diversity function for shannon diveristy index (increases as diversity increases)
```{r}
div_shanR1<-diversity(vegReadyR1, index = "shannon")
div_shanR2<-diversity(vegReadyR2, index = "shannon")
div_shanR3<-diversity(vegReadyR3, index = "shannon")
div_shanR4<-diversity(vegReadyR4, index = "shannon")
```

Do the same for the simpson's index (similarity index- take 1-S to find diversity index). Measurement of probability that any two randomly selected individuals from infinitely large community will belong to same species.
```{r}
div_simpR1<- diversity(vegReadyR1, index = "simpson")
div_simpR2<- diversity(vegReadyR2, index = "simpson")
div_simpR3<- diversity(vegReadyR3, index = "simpson")
div_simpR4<- diversity(vegReadyR4, index = "simpson")

inv_simpR1<- diversity(vegReadyR1, index = "invsimpson")
inv_simpR2<- diversity(vegReadyR2, index = "invsimpson")
inv_simpR3<- diversity(vegReadyR3, index = "invsimpson")
inv_simpR4<- diversity(vegReadyR4, index = "invsimpson")
```

Create DF with round # in one column and diversity in another. 
```{r}
library(tidyr)
ForestR1<- unique(divVeganR1$ForestName)
shanDivR1<- as.data.frame(cbind(div_shanR1, ForestR1))
ForestR2<- unique(divVeganR2$ForestName)
shanDivR2<- as.data.frame(cbind(div_shanR2, ForestR2))
ForestR3<- unique(divVeganR3$ForestName)
shanDivR3<- as.data.frame(cbind(div_shanR3, ForestR3))
ForestR4<- unique(divVeganR4$ForestName)
shanDivR4<- as.data.frame(cbind(div_shanR4, ForestR4))

```

Plot bar graph of Shannon Index Diversity
```{r}
shanDivR1$Type<- as.factor(c("D","P","D","D","P","P"))
shanDivR1$div_shan<- as.numeric(as.character(shanDivR1$div_shanR1))
ggplot(shanDivR1, aes(x= ForestR1, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Forest") +
     ylab("Shannon Diversity Index")

ggsave("Shannon_Diversity_Index_ForestR1.jpg", device= "jpg")
write.csv(shanDivR1, file = "ShanDivForestR1.csv")

shanDivR2$Type<- as.factor(c("D","P","D","D","P","P"))
shanDivR2$div_shan<- as.numeric(as.character(shanDivR2$div_shanR2))
ggplot(shanDivR2, aes(x= ForestR2, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Forest") +
     ylab("Shannon Diversity Index") 

ggsave("Shannon_Diversity_Index_ForestR2.jpg", device= "jpg")
write.csv(shanDivR2, file = "ShanDivForestR2.csv")

shanDivR3$Type<- as.factor(c("P","D","D","P","P"))
shanDivR3$div_shan<- as.numeric(as.character(shanDivR3$div_shanR3))
ggplot(shanDivR3, aes(x= ForestR3, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Forest") +
     ylab("Shannon Diversity Index")

ggsave("Shannon_Diversity_Index_ForestR3.jpg", device= "jpg")
write.csv(shanDivR3, file = "ShanDivForestR3.csv")

shanDivR4$Type<- as.factor(c("D","P","D","D","P","P"))
shanDivR4$div_shan<- as.numeric(as.character(shanDivR4$div_shanR4))
ggplot(shanDivR4, aes(x= ForestR4, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Forest") +
     ylab("Shannon Diversity Index")

ggsave("Shannon_Diversity_Index_ForestR4.jpg", device= "jpg")
write.csv(shanDivR4, file = "ShanDivForestR4.csv")
```

Do the same for Simpson's Index
```{r}
simpDivR1<-as.data.frame(cbind(div_simpR1, ForestR1))
simpDivR1$Type<- as.factor(c("D","P","D","D","P","P"))

simpDivR1$div_simp<- as.numeric(as.character(simpDivR1$div_simpR1))
ggplot(simpDivR1, aes(x= ForestR1, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_ForestR1.jpg", device = "jpg")
write.csv(simpDivR1, file = "SimpDivForestR1.csv")

simpDivR2<-as.data.frame(cbind(div_simpR2, ForestR2))
simpDivR2$Type<- as.factor(c("D","P","D","D","P","P"))

simpDivR2$div_simp<- as.numeric(as.character(simpDivR2$div_simpR2))
ggplot(simpDivR2, aes(x= ForestR2, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_ForestR2.jpg", device = "jpg")
write.csv(simpDivR2, file = "SimpDivForestR2.csv")

simpDivR3<-as.data.frame(cbind(div_simpR3, ForestR3))
simpDivR3$Type<- as.factor(c("P","D","D","P","P"))

simpDivR3$div_simp<- as.numeric(as.character(simpDivR3$div_simpR3))
ggplot(simpDivR3, aes(x= ForestR3, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_ForestR3.jpg", device = "jpg")
write.csv(simpDivR3, file = "SimpDivForestR3.csv")

simpDivR4<-as.data.frame(cbind(div_simpR4, ForestR4))
simpDivR4$Type<- as.factor(c("D","P","D","D","P","P"))

simpDivR4$div_simp<- as.numeric(as.character(simpDivR4$div_simpR4))
ggplot(simpDivR4, aes(x= ForestR4, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_ForestR4.jpg", device = "jpg")
write.csv(simpDivR4, file = "SimpDivForestR4.csv")

```

Inverse Simpson's Index
```{r}
InvSimpR1<-as.data.frame(cbind(inv_simpR1, ForestR1))
InvSimpR1$Type<- as.factor(c("D","P","D","D","P","P"))

InvSimpR1$inv_simp<- as.numeric(as.character(InvSimpR1$inv_simpR1))
ggplot(InvSimpR1, aes(x= ForestR1, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_ForestR1.jpg", device = "jpg")
write.csv(InvSimpR1, file = "InvSimpForestR1.csv")

InvSimpR2<-as.data.frame(cbind(inv_simpR2, ForestR2))
InvSimpR2$Type<- as.factor(c("D","P","D","D","P","P"))

InvSimpR2$inv_simp<- as.numeric(as.character(InvSimpR2$inv_simpR2))
ggplot(InvSimpR2, aes(x= ForestR2, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_ForestR2.jpg", device = "jpg")
write.csv(InvSimpR2, file = "InvSimpForestR2.csv")

InvSimpR3<-as.data.frame(cbind(inv_simpR3, ForestR3))
InvSimpR3$Type<- as.factor(c("P","D","D","P","P"))

InvSimpR3$inv_simp<- as.numeric(as.character(InvSimpR3$inv_simpR3))
ggplot(InvSimpR3, aes(x= ForestR3, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_ForestR3.jpg", device = "jpg")
write.csv(InvSimpR3, file = "InvSimpForestR3.csv")

InvSimpR4<-as.data.frame(cbind(inv_simpR4, ForestR4))
InvSimpR4$Type<- as.factor(c("D","P","D","D","P","P"))

InvSimpR4$inv_simp<- as.numeric(as.character(InvSimpR4$inv_simpR4))
ggplot(InvSimpR4, aes(x= ForestR4, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_ForestR4.jpg", device = "jpg")
write.csv(InvSimpR4, file = "InvSimpForestR4.csv")
```








Calculate diversity per camera per season 
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)

DF<- read_csv("~/Documents/Kate_ThesisCode/dataFinal.csv")
#This adds a unique camera ID column to the DF, which will be important when you are calculating diversity per camera per season. This column takes the unit#_SD#_forest
DF$CamID<-substr(DF$Imj1, 1,8)

dump<-which(DF$choice == "NOTHINGHERE" | DF$choice == "SOMETHINGHERE" | DF$choice == "HUMAN" | DF$choice == "GROUSERUFFED" | DF$choice == "CROWORRAVEN" | DF$choice == "OTHERBIRD" | DF$choice == "DOMESTICDOG" | DF$choice == "OWL" | DF$choice == "BLUEJAY" | DF$choice == "TURKEY" | DF$choice == "GOOSEWILD")

#now dump
DF<-DF[-dump,]

Round1<-filter(DF, round==1)
Round2<- filter(DF, round==2)
Round3<- filter(DF, round==3)
Round4<- filter(DF, round==4)
```

```{r}

diversityR1<-Round1 %>% group_by(CamID, choice) %>% summarise(
	NumEvents = length(CamID)
)
diversityR2<-Round2 %>% group_by(CamID, choice) %>% summarise(
	NumEvents = length(CamID)
)
diversityR3<-Round3 %>% group_by(CamID, choice) %>% summarise(
	NumEvents = length(CamID)
)
diversityR4<-Round4 %>% group_by(CamID, choice) %>% summarise(
	NumEvents = length(CamID)
)

library(tidyr)
divVeganR1<- spread(diversityR1, choice, NumEvents)
divVeganR2<- spread(diversityR2, choice, NumEvents)
divVeganR3<- spread(diversityR3, choice, NumEvents)
divVeganR4<- spread(diversityR4, choice, NumEvents)
```

Now, for vegan, replace NA's with zero and also delete the first column.
```{r}
#replace NAs with zeros
divVeganR1[is.na(divVeganR1)] <- 0
divVeganR2[is.na(divVeganR2)] <- 0
divVeganR3[is.na(divVeganR3)] <- 0
divVeganR4[is.na(divVeganR4)] <- 0

#dump first column
vegReadyR1<-divVeganR1[,-1]
vegReadyR2<-divVeganR2[,-1]
vegReadyR3<-divVeganR3[,-1]
vegReadyR4<-divVeganR4[,-1]
```

Run the diversity function for shannon diveristy index (increases as diversity increases)
```{r}
div_shanR1<-diversity(vegReadyR1, index = "shannon")
div_shanR2<-diversity(vegReadyR2, index = "shannon")
div_shanR3<-diversity(vegReadyR3, index = "shannon")
div_shanR4<-diversity(vegReadyR4, index = "shannon")
```

Do the same for the simpson's index (similarity index- take 1-S to find diversity index). Measurement of probability that any two randomly selected individuals from infinitely large community will belong to same species.
```{r}
div_simpR1<- diversity(vegReadyR1, index = "simpson")
div_simpR2<- diversity(vegReadyR2, index = "simpson")
div_simpR3<- diversity(vegReadyR3, index = "simpson")
div_simpR4<- diversity(vegReadyR4, index = "simpson")

inv_simpR1<- diversity(vegReadyR1, index = "invsimpson")
inv_simpR2<- diversity(vegReadyR2, index = "invsimpson")
inv_simpR3<- diversity(vegReadyR3, index = "invsimpson")
inv_simpR4<- diversity(vegReadyR4, index = "invsimpson")
```

Create DF with round # in one column and diversity in another. 
```{r}
library(tidyr)
CamsR1<- unique(divVeganR1$CamID)
shanDivR1<- as.data.frame(cbind(div_shanR1, CamsR1))
CamsR2<- unique(divVeganR2$CamID)
shanDivR2<- as.data.frame(cbind(div_shanR2, CamsR2))
CamsR3<- unique(divVeganR3$CamID)
shanDivR3<- as.data.frame(cbind(div_shanR3, CamsR3))
CamsR4<- unique(divVeganR4$CamID)
shanDivR4<- as.data.frame(cbind(div_shanR4, CamsR4))

```

Plot bar graph of Shannon Index Diversity
```{r}
shanDivR1$Type<- as.factor(c("D","P", "P", "D","D","P","D", "P", "D", "P", "D", "D", "D","D", "P", "P", "P", "P", "P"))
shanDivR1$div_shan<- as.numeric(as.character(shanDivR1$div_shanR1))
ggplot(shanDivR1, aes(x= CamsR1, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Camera") +
     ylab("Shannon Diversity Index")

ggsave("Shannon_Diversity_Index_CamsR1.jpg", device= "jpg")
write.csv(shanDivR1, file = "ShanDivCamsR1.csv")

shanDivR2$Type<- as.factor(c("P", "D","P","P", "D","D","P","D", "P","D", "P", "D","D","D","D", "P","P","D","P","P","P"))
shanDivR2$div_shan<- as.numeric(as.character(shanDivR2$div_shanR2))
ggplot(shanDivR2, aes(x= CamsR2, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Camera") +
     ylab("Shannon Diversity Index") 

ggsave("Shannon_Diversity_Index_CamsR2.jpg", device= "jpg")
write.csv(shanDivR2, file = "ShanDivCamsR2.csv")

shanDivR3$Type<- as.factor(c("D","D","P", "P","D","D", "P","P","P","D"))
shanDivR3$div_shan<- as.numeric(as.character(shanDivR3$div_shanR3))
ggplot(shanDivR3, aes(x= CamsR3, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Camera") +
     ylab("Shannon Diversity Index")

ggsave("Shannon_Diversity_Index_CamsR3.jpg", device= "jpg")
write.csv(shanDivR3, file = "ShanDivCamsR3.csv")

shanDivR4$Type<- as.factor(c("P", "D","P","D","P","P", "D","D", "D", "P","D","D","D","D","D", "P", "P", "P", "P", "D", "P", "P"))
shanDivR4$div_shan<- as.numeric(as.character(shanDivR4$div_shanR4))
ggplot(shanDivR4, aes(x= CamsR4, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Camera") +
     ylab("Shannon Diversity Index")

ggsave("Shannon_Diversity_Index_CamsR4.jpg", device= "jpg")
write.csv(shanDivR4, file = "ShanDivCamsR4.csv")
```

Do the same for Simpson's Index
```{r}
simpDivR1<-as.data.frame(cbind(div_simpR1, CamsR1))
simpDivR1$Type<- as.factor(c("D","P", "P", "D","D","P","D", "P", "D", "P", "D", "D", "D","D", "P", "P", "P", "P", "P"))

simpDivR1$div_simp<- as.numeric(as.character(simpDivR1$div_simpR1))
ggplot(simpDivR1, aes(x= CamsR1, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_CamsR1.jpg", device = "jpg")
write.csv(simpDivR1, file = "SimpDivCamsR1.csv")

simpDivR2<-as.data.frame(cbind(div_simpR2, CamsR2))
simpDivR2$Type<- as.factor(c("P", "D","P","P", "D","D","P","D", "P","D", "P", "D","D","D","D", "P","P","D","P","P","P"))

simpDivR2$div_simp<- as.numeric(as.character(simpDivR2$div_simpR2))
ggplot(simpDivR2, aes(x= CamsR2, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_CamsR2.jpg", device = "jpg")
write.csv(simpDivR2, file = "SimpDivCamsR2.csv")

simpDivR3<-as.data.frame(cbind(div_simpR3, CamsR3))
simpDivR3$Type<- as.factor(c("D","D","P", "P","D","D", "P","P","P","D"))

simpDivR3$div_simp<- as.numeric(as.character(simpDivR3$div_simpR3))
ggplot(simpDivR3, aes(x= CamsR3, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_CamsR3.jpg", device = "jpg")
write.csv(simpDivR3, file = "SimpDivCamsR3.csv")

simpDivR4<-as.data.frame(cbind(div_simpR4, CamsR4))
simpDivR4$Type<- as.factor(c("P", "D","P","D","P","P", "D","D", "D", "P","D","D","D","D","D", "P", "P", "P", "P", "D", "P", "P"))

simpDivR4$div_simp<- as.numeric(as.character(simpDivR4$div_simpR4))
ggplot(simpDivR4, aes(x= CamsR4, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index_CamsR4.jpg", device = "jpg")
write.csv(simpDivR4, file = "SimpDivCamsR4.csv")

```

Inverse Simpson's Index
```{r}
InvSimpR1<-as.data.frame(cbind(inv_simpR1, CamsR1))
InvSimpR1$Type<- as.factor(c("D","P", "P", "D","D","P","D", "P", "D", "P", "D", "D", "D","D", "P", "P", "P", "P", "P"))

InvSimpR1$inv_simp<- as.numeric(as.character(InvSimpR1$inv_simpR1))
ggplot(InvSimpR1, aes(x= CamsR1, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_CamsR1.jpg", device = "jpg")
write.csv(InvSimpR1, file = "InvSimpCamsR1.csv")

InvSimpR2<-as.data.frame(cbind(inv_simpR2, CamsR2))
InvSimpR2$Type<- as.factor(c("P", "D","P","P", "D","D","P","D", "P","D", "P", "D","D","D","D", "P","P","D","P","P","P"))

InvSimpR2$inv_simp<- as.numeric(as.character(InvSimpR2$inv_simpR2))
ggplot(InvSimpR2, aes(x= CamsR2, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_CamsR2.jpg", device = "jpg")
write.csv(InvSimpR2, file = "InvSimpCamsR2.csv")

InvSimpR3<-as.data.frame(cbind(inv_simpR3, CamsR3))
InvSimpR3$Type<- as.factor(c("D","D","P", "P","D","D", "P","P","P","D"))

InvSimpR3$inv_simp<- as.numeric(as.character(InvSimpR3$inv_simpR3))
ggplot(InvSimpR3, aes(x= CamsR3, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_CamsR3.jpg", device = "jpg")
write.csv(InvSimpR3, file = "InvSimpCamsR3.csv")

InvSimpR4<-as.data.frame(cbind(inv_simpR4, CamsR4))
InvSimpR4$Type<- as.factor(c("P", "D","P","D","P","P", "D","D", "D", "P","D","D","D","D","D", "P", "P", "P", "P", "D", "P", "P"))

InvSimpR4$inv_simp<- as.numeric(as.character(InvSimpR4$inv_simpR4))
ggplot(InvSimpR4, aes(x= CamsR4, y = inv_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Camera") +
     ylab("Inverse Simpson's Diversity Index")

ggsave("Inv_Simpson's_Diversity_Index_CamsR4.jpg", device = "jpg")
write.csv(InvSimpR4, file = "InvSimpCamsR4.csv")
```

Let's make some graphs
```{r}
Diversity_total <- read_csv("~/Documents/Kate_ThesisCode/Diversity_total.csv")

Diversity_total$BC<-replace(Diversity_total$BC, is.na(Diversity_total$BC), 0)
Diversity_total$Season<-factor(Diversity_total$Season,c(1,2,3,4), labels = c("Winter", "Spring", "Summer", "Fall"))

BC<-ggplot(Diversity_total, aes(x= Season, y = BC, fill = Diversity_Indices)) + 
     geom_bar(stat = "identity",position= position_dodge(), width = 0.7) + labs(title = "Beaver Creek", x= "Season", y= "Diversity Indices") + theme (plot.title =element_text(hjust = 0.5))
BC<- BC + coord_cartesian(ylim = c(0,14))

SH<-ggplot(Diversity_total, aes(x= Season, y = SH, fill = Diversity_Indices)) + 
     geom_bar(stat = "identity",position= position_dodge(), width = 0.7) +
    labs(title = "South Hammond", x= "Season", y= "Diversity Indices") + theme (plot.title =element_text(hjust = 0.5))
SH<- SH + coord_cartesian(ylim = c(0,14))

DON<-ggplot(Diversity_total, aes(x= Season, y = DON, fill = Diversity_Indices)) + 
     geom_bar(stat = "identity",position= position_dodge(), width = 0.7) +
    labs(title = "Donnerville", x= "Season", y= "Diversity Indices") + theme (plot.title =element_text(hjust = 0.5))
DON<- DON + coord_cartesian(ylim = c(0,14)) 

DEG<-ggplot(Diversity_total, aes(x= Season, y = DEG, fill = Diversity_Indices)) + 
     geom_bar(stat = "identity",position= position_dodge(), width = 0.7) +
     labs(title = "Degrasse", x= "Season", y= "Diversity Indices") + theme (plot.title =element_text(hjust = 0.5))
DEG<- DEG + coord_cartesian(ylim = c(0,14))

WF<-ggplot(Diversity_total, aes(x= Season, y = WF, fill = Diversity_Indices)) + 
     geom_bar(stat = "identity",position= position_dodge(), width = 0.7) +
     labs(title = "Whiskey Flats", x= "Season", y= "Diversity Indices") + theme (plot.title =element_text(hjust = 0.5))
WF<- WF + coord_cartesian(ylim = c(0,14))
WHIP<-ggplot(Diversity_total, aes(x= Season, y = WHIP, fill = Diversity_Indices)) + 
     geom_bar(stat = "identity",position= position_dodge(), width = 0.7) +
     labs(title = "Whippoorwill Corners", x= "Season", y= "Diversity Indices") + theme (plot.title =element_text(hjust = 0.5))
WHIP<- WHIP + coord_cartesian(ylim = c(0,14))

TOTAL<-ggarrange(BC,SH,DON,DEG,WF,WHIP, ncol = 3, nrow = 2, legend = "right", common.legend = TRUE)


ggsave("Div_Forests.jpg", device = "jpg")
```

