---
title: 'Image Pre-processing 1: Assign images to events when dates are messed up'
output:
  html_document:
    df_print: paged
---
##Introduction
This is the R code needed to use the metadata from a folder of images to compare the image time stamps and group images into their respective "events." It is a special set of code, in that it can be used for (and ONLY for) sets of images in which the date in the game camera reset to the factory default when the camera was deployed, and for which we have tried to correct the dates using exiftool.  **Do not use this file for a set of images for which the dates were recorded correctly on the cameras!**

An event is a set of pictures taken within a time threshold.  We set our cameras to take up to 3 pictures in a bout, and set them with a 1 minute delay before they can take more pictures, so we can use 1 minute as our threshold.

###Before you begin

In order to run this code, you will need to have the following in place:

* A folder with a set of images (and only images) in it.
* A csv file made using *exiftool* that has date/time metadata from all of the photos in the folder


###Step 1
Set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(readr)
library(lubridate)
```
###Step 2
Now we need to pull in the image metadata.  It was generated and saved as a .csv outside of R using a tool called *exiftool* that is run from the command line.  We should see if we can get *exiftool* installed on the HPC. It works to run exiftool within R (library(exiftool)), but it is VERY VERY SLOW. 

```{r}
#library(readr) if not called at top of code
#eta <- read.csv("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Kate/R1B2.csv") 
#obvioulsly, put correct file name here
Meta <- read.csv("~/Dropbox/Zooniverse_work/Kate/R1B2.csv")
```

###Step 3
Now that we have the metadata, we can see that the DateTimeOriginal column came in as a factor.  Let's change it with lubridate.  Note that then a very important step is to ORDER the data frame in terms of date/time.  If you fail to order the data frame, when you compare dates/times you will get incorrect output.

```{r}
#library(lubridate)if not called at top of code 
Meta$DateTimeOriginal<-ymd_hms(Meta$DateTimeOriginal)
#Meta<-Meta[order(Meta$DateTimeOriginal, Meta$FileName),]#THIS IS KEY
```
###Step 4
Need to filter by camera.  First make new camera number variable.

```{r}
#first make Fielname a chr var
Meta$FileName<-as.character(Meta$FileName)
Meta$cam_num<-substr(Meta$FileName, 1, 5) #grabs the first through fifth characters from the file name
cams<-unique(Meta$cam_num)
```

Next, create a loop to filter and process by camera

```{r}
#set some initial parameters
maxEvent<-1
thresh<-5

for (i in 1:length(cams)){
  #subset the DF by camera
  tempDF<-filter(Meta, cam_num == cams[i])
  tempDF
  tempDF<-tempDF[order(tempDF$FileName),] #make sure in order of filename and not time
  #now we have the subset; need to process using old code
  
  #calculate time differences for tempDF
  MyDiffs<-diff(tempDF$DateTimeOriginal)#returns what looks like an empty variable in the environment window
  MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data
  #Now let's see if we can assign images to events using this logic.  We will need to set the time threshold    to something very short since dates/times are messed up (camera reset). Try 5 seconds.
  
  #thresh<-5 #set a threshold for number of seconds between events
  ev<-vector()
  L<-length(tempDF$DateTimeOriginal)
  
    for(x in 1:L){
      interval<-diff(tempDF$DateTimeOriginal)
      ev<-1; Event_num<-numeric() 
      #created new var called ev and set to 1, created empty numeric vector called Event_num. 
      #Event_num will store the assigned event for each image
    }       
  cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
    if (i == 1) ev<-1 else ev<-maxEvent    
    
    for(z in 1:(L-1)){#this is where the problem is; resets event numbers
      if(!cond[z]) ev<-ev else ev<-ev+1
      Event_num<-c(Event_num,ev) 
    }
    Event<-c(maxEvent,Event_num)
           
    tempDF$Event<-Event
    #newDF<-tempDF
    #testing saving each DF
    #name<-paste0("NewDF", i)
    
    if (i == 1) {
      newDF <- tempDF} else {
      newDF<- rbind(newDF, tempDF)
    }
    maxEvent<-(max(newDF$Event)+1)
}
    
#Now write output
#write.csv(newDF,"/Volumes/External Drive/Dropbox/R/Zooniverse_work/Output/Images_by_event_Date_Issues.csv")
write.csv(newDF,"~Dropbox/Zooniverse_work/Output/Images_by_event_Date_Issues.csv")
```
And it works!
