---
title: "Na誰ve Occupancy Final"
output: html_notebook
---
Naive Occupancy is the percent of cameras at which a species occurs

Use this code to calculate Naive Occupancy. 

Load necessary packages and clear the environment
```{r}
rm(list=ls())

library(dplyr)
library(tidyverse)
library(tidyr)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers
```

Import the masterDF
```{r}
masterDF1 <- read_csv("~/Dropbox/Zooniverse_work/Kate/masterDF.csv")
masterDF <- read_csv("~/Documents/Kate_ThesisCode/masterDF_test.csv") #masterDF_test.csv is 'masterDF.csv' with manual modifications to add round number to the end of Sampling.Unit.Name. There was an issue with repeating cameras from different rounds not being accounted for. 

masterDF$Sampling.Event<-2020.1
masterDF$Start.Date<-mdy(masterDF$Start.Date)
masterDF$End.Date<-mdy(masterDF$End.Date)
```

Source functions from Wild.ID chapters
```{r}
source('~/Dropbox/Zooniverse_work/Camera_Trapping_Ch5_Work/TEAM library 1.7.R')
```

```{r}
#masterDF$Start.Date<-mdy(masterDF$Start.Date)
#masterDF$End.Date<-mdy(masterDF$End.Date)
masterDF$td.photo<-as.POSIXct(masterDF$td.photo,format="%Y:%m:%d %H:%M:%S")
masterDF$Photo.Date<-mdy(masterDF$Photo.Date)
```


Na誰ve Occupancy Calculation
```{r}
mat<-f.matrix.creator(masterDF)
naive_occu_2020<-naive(mat)

```
Check Naive Occupancy to see if this calculation is correct
```{r}
Check<- masterDF %>% group_by(bin) %>% summarise(
  cams= n_distinct(Sampling.Unit.Name)
)
#It looks like the naive occupancy function calculates the values pretty much the same as manual calculation, but not exact enough that I feel confident in this. 
```

Calculate RAI manually. RAI = events / camera trapping days
```{r}
RAI<- masterDF %>% group_by(bin) %>% summarise(
  cams= n_distinct(Event)
)
```


```{r}
events.sp<-event.sp(masterDF, year = 2020.1, thresh = 60)
```

Calculate Na誰ve Occupancy per season
```{r}
OccWinter<-masterDF %>% group_by(round) %>% filter(round==1)
OccSpring<- masterDF %>% group_by(round) %>% filter(round==2)
OccSummer<- masterDF %>% group_by(round) %>% filter(round==3)
OccFall<-masterDF %>% group_by(round) %>% filter(round==4)

matWinter<-f.matrix.creator(OccWinter)
naive_occu_2020_W<-naive(matWinter)


matSpring<-f.matrix.creator(OccSpring)
naive_occu_2020_Sp<-naive(matSpring)

matSummer<-f.matrix.creator(OccSummer)
naive_occu_2020_S<-naive(matSummer)

matFall<-f.matrix.creator(OccFall)
naive_occu_2020_F<-naive(matFall)
```

Calculate Na誰ve Occupancy by forest type

```{r}
Join<-read_csv("~/Documents/Kate_ThesisCode/dataFinal.csv")
Join1<-select(Join, "Imj1", "ForestType", "round", "choice")
masterDFforest<-left_join(masterDF, Join, by = c("Event"= "Imj1", "round", "bin"="choice"))

Pine<-filter(masterDFforest, ForestType == "Pine")
Deciduous<-filter(masterDFforest, ForestType== "Deciduous")

matPine<-f.matrix.creator(Pine)
naive_occu_2020_Pine<-naive(matPine)

matDecid<-f.matrix.creator(Deciduous)
naive_occu_2020_Decid<-naive(matDecid)
```

