---
title: "Species Richness "
output: html_notebook
---

The goal of this R Notebook is to calculate species richness from the data generated in Zooniverse. 

```{r}
#Basic Parameters 
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)

#Upload the dataset 
DF<- read.csv("~/Documents/Kate_ThesisCode/dataFinal.csv")

DF$CamID<-substr(DF$Imj1, 1,8)

#Quick glimpse of the data
glimpse(DF)
```

Now get rid of the "NOTHINGHERE" and "SOMETHINGHERE" and other species that are not mammals since they provide no species information.

```{r}
dump<-which(DF$choice == "NOTHINGHERE" | DF$choice == "SOMETHINGHERE" | DF$choice == "HUMAN" | DF$choice == "GROUSERUFFED" | DF$choice == "CROWORRAVEN" | DF$choice == "OTHERBIRD" | DF$choice == "DOMESTICDOG" | DF$choice == "OWL" | DF$choice == "BLUEJAY" | DF$choice == "TURKEY" | DF$choice == "GOOSEWILD")

#now dump
DF<-DF[-dump,]
```

Total species richness for all 6 forests
```{r}
TOT_richness <- DF %>% group_by(ForestType) %>% summarise(
  Number_distinct_species = n_distinct(choice),
  Species_observed = n()
)

```

Species Richness per Forest 
```{r}
Forest_richness <- DF %>% group_by(ForestName) %>% summarise(
  Number_species = n_distinct(choice)
  )

```

Species Richness by camera 
```{r}
Camera_richness <- DF %>% group_by(CamID, round) %>% summarise(
  Number_species = n_distinct(choice)
  )

```

Graph 
```{r}
#Number of species observed 
ggplot(DF, aes(x = choice, fill = ForestType)) + geom_histogram(stat = "count", position = "dodge") + theme_bw() + theme(
  axis.text.x = element_text(angle = 90, size = 10, vjust = 0.5)
)

```

Overall species richness among all forests in all seasons
```{r}
Choices<- DF %>% group_by(choice) %>% summarise(
  species= n()
)
```

Deer count per camera
```{r}
Deer<-filter(DF, choice== "DEERWHITETAILED")
DeerNum<- Deer %>% group_by(CamID, round) %>% summarise(
  species= n()
)
```

Fisher count per camera
```{r}
Fisher<-filter(DF, choice== "FISHER")
FisherNum<- Fisher %>% group_by(CamID, round) %>% summarise(
  species= n()
)
```

Black Bear count per camera
```{r}
Bear<-filter(DF, choice== "BLACKBEAR")
BearNum<- Bear %>% group_by(CamID, round) %>% summarise(
  species= n()
)
```

Red Fox count per camera
```{r}
Fox<-filter(DF, choice== "FOXRED")
FoxNum<- Fox %>% group_by(CamID, round) %>% summarise(
  species= n()
)
```

Graph species richness per forest per season and color by forest type 
```{r}
ForestSeason<- DF %>% group_by(ForestName, round, ForestType) %>% summarise(
  Species = n_distinct(choice)
)


ggplot(ForestSeason, aes(x= round, y = Species, group = ForestType, color = ForestType)) + 
     geom_col(position= "dodge") +
     xlab("Forests per Season") +
     ylab("Species Richness") + facet_grid(col = vars(ForestName))  + labs(fill = "Forest Type")



ggsave("ForestSeason_SR.jpg", device = "jpg")

```


Species richness by season
```{r}
Season<- DF %>% group_by(round) %>% summarise(
  species= n_distinct(choice)
)

ggplot(Season, aes(x= round, y = species)) + 
     geom_col(position= "dodge") +
     xlab("Season") +
     ylab("Species Richness") 

ggsave("Season_SR.jpg", device = "jpg")
```

Graph species richness per camera per forest per season and color by forest type
```{r}
CamsForestSeason<- DF %>% group_by(CamID, ForestName, round, ForestType) %>% summarise(
  Species = n_distinct(choice)
)


ggplot(CamsForestSeason, aes(x= round, y = Species, group = ForestType, color = ForestType)) + 
     geom_col(position= "dodge") +
     xlab("Forests per Season") +
     ylab("Species Richness") + 
  facet_grid(col = vars(ForestName))   +  geom_text(aes(label = CamID), size = 1.5) + labs(fill = "Forest Type")




ggsave("ForestSeason_SR.jpg", device = "jpg")
```
