---
title: "Species Accumulation Curve"
output: html_notebook
---
Species accumulation curve can indicate if we deployed an adequate sampling effort.

Use this code to calculate species accumulation curve. 

Load necessary packages and clear the environment
```{r}
rm(list=ls())

library(dplyr)
library(tidyverse)
library(tidyr)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers
```

Import the masterDF
```{r}
masterDF1 <- read_csv("~/Dropbox/Zooniverse_work/Kate/masterDF.csv")
masterDF <- read_csv("~/Documents/Kate_ThesisCode/dataFinal.csv")
#dataFinal.csv is "joinedData.csv" that was manually cleaned, removing all subjects that we did not want to count (from cameras that misfired or malfunctioned, etc). "dataFinal.csv" also has the actual dates of deployment, shown in the 'Use_End_Date' column based on the notes from "Came_Use_Date.csv". Be sure to remove Lampson Falls from the data frame because we are not using that forest in this study. 

#I needed to do a lot of manual modifications to this data frame. In addition to all the date modifications and camera/image removals, I had to go in an manually adjust some camera names, including changing .jpg to .JPG on the '03_05_SH' Round 3 images. I'm not sure why it did that. To avoid making a bunch of tiny error that become a big deal later on, be sure to really check the field sheets and make sure the main data sets (like Cam_Use_Date and Metadata_Field_Sheet) are correct!

```

Source functions from Wild.ID chapters in console
```{r}
source('~/Dropbox/Zooniverse_work/Camera_Trapping_Ch5_Work/TEAM library 1.7.R')
```

Now get rid of the "NOTHINGHERE" and "SOMETHINGHERE" and other species that are not mammals since they provide no species information.

```{r}
dump<-which(masterDF$choice == "NOTHINGHERE" | masterDF$choice == "SOMETHINGHERE" | masterDF$choice == "HUMAN" | masterDF$choice == "GROUSERUFFED" | masterDF$choice == "CROWORRAVEN" | masterDF$choice == "OTHERBIRD" | masterDF$choice == "DOMESTICDOG" | masterDF$choice == "OWL" | masterDF$choice == "BLUEJAY" | masterDF$choice == "TURKEY" | masterDF$choice == "GOOSEWILD")

#now dump
masterDF<-masterDF[-dump,]
```



Calculate camera trap nights
```{r}
masterDF$Date_Out<- mdy(masterDF$Date_Out)
masterDF$Use_End_Date<-mdy(masterDF$Use_End_Date)


masterDF$Camera_Trap_Days<- difftime(masterDF$Use_End_Date, masterDF$Date_Out , units = c("days"))
```

Need to bring in photo date and time. This will come from the exif data gathered from the photo metadata. Need to merge these files. 
```{r}
#New<-select(masterDF, "subject_ids", "diff_species", "choice", "Imj1", "CamNum", "SD_card_num", "ForestType", "ForestName", "Date_Out", "Use_End_Date", "Camera_Trap_Days", "round")

New<-select(masterDF, "choice", "Imj1", "CamNum", "SD_card_num", "ForestType", "ForestName", "Date_Out", "Use_End_Date", "Camera_Trap_Days", "round")
```

Now we need to bring in the photo dates, because the functions we are using come from the Wild.ID format "Chapter 5" business. They require photo date and time, which we will distinguish as "td.photo", "Photo.Date", and "Photo.Time". To get photo date and time, you have to generate a csv file of all of the images you uploaded to Zooniverse. Use the Terminal to generate a csv of the photo metadata and there should be a column titled "DateTimeOriginal". From that output csv, you only need the columns "FileName" and "DateTimeOriginal". Now we can join the photo dates and times to our masterDF
```{r}
PhotoDatesTimes <- read_csv("~/Documents/Kate_ThesisCode/PhotoDatesTimes.csv") #This is the df generated from the Terminal and then cut down to have just the necessary columns.

#Need to carry round # over with you when you join!
dfPrep<-left_join(New, PhotoDatesTimes, by=c("Imj1"="FileName", "round"="Round"), type='right', match='all')

```

Separate out photo dates and times into different columns. Maintain one column with both dates and times together. 
```{r}
dfPrep$Photo.Time <- format(as.POSIXct(dfPrep$DateTimeOriginal,format="%Y:%m:%d %H:%M:%S"),"%H:%M:%S")

dfPrep$Photo.Date <- format(as.POSIXct(dfPrep$DateTimeOriginal,format="%Y:%m:%d %H:%M:%S"),"%m/%d/%Y")

#dfPrep$Photo.Time<-hms(dfPrep$Photo.Time)
```

Change "Date_Out" and "Use_End_Date" columns to character variables and reformat the dates.
```{r}
dfPrep$Use_End_Date<-format(dfPrep$Use_End_Date, "%m/%d/%Y")
dfPrep$Date_Out<-format(dfPrep$Date_Out, "%m/%d/%Y")
```


Change the names of the columns to match that which Wild.ID requires. 
```{r}
#SpeciesAcc<-select(dfPrep, "subject_ids", "Imj1", "DateTimeOriginal", "Camera_Trap_Days", "Date_Out", "Use_End_Date", "choice", "Photo.Date", "Photo.Time", "Photo.Date", "round")

dfPrep$Sampling.Unit.Name<-substr(dfPrep$Imj1, 1,8)

SpeciesAcc<-select(dfPrep, "Sampling.Unit.Name", "Imj1", "DateTimeOriginal", "Camera_Trap_Days", "Date_Out", "Use_End_Date", "choice", "Photo.Date", "Photo.Time", "Photo.Date", "round")

names(SpeciesAcc)<- c("Sampling.Unit.Name", "Event", "td.photo", "ndays", "Start.Date", "End.Date", "bin", "Photo.Date", "Photo.Time", "round")
```


Subset the data by season and add in sampling event number based on round.
```{r}
SpeciesAccWinter<-SpeciesAcc %>% group_by(round) %>% filter(round==1)
SpeciesAccSpring<- SpeciesAcc %>% group_by(round) %>% filter(round==2)
SpeciesAccSummer<- SpeciesAcc %>% group_by(round) %>% filter(round==3)
SpeciesAccFall<-SpeciesAcc %>% group_by(round) %>% filter(round==4)
```


Add a column called "Sampling.Event" filled with 2020.1
```{r}
SpeciesAccWinter$Sampling.Event<-2020.1
SpeciesAccSpring$Sampling.Event<-2020.2
SpeciesAccSummer$Sampling.Event<-2020.3
SpeciesAccFall$Sampling.Event<-2020.4
```

Get rid of the "round" column to match Wild.ID formatting
```{r}
SpeciesAccWinter<- SpeciesAccWinter[,-(10)]
SpeciesAccSpring<- SpeciesAccSpring[,-(10)]
SpeciesAccSummer<- SpeciesAccSummer[,-(10)]
SpeciesAccFall<- SpeciesAccFall[,-(10)]
```

Write this csv file because its formatting can be used for other R scripts.
```{r}
write.csv(SpeciesAcc, file = "masterDF.csv")

#Once you write this csv file, you need to manually adjust the 'Sampling.Unit.Name' to add in the round number. This will help distinguish repeating Cam_SDCard_Forests (because that happens sometimes).
```


Species Accumulation for winter season
```{r}
#need to change all dates to date format, and need to change all times to time format. Not sure exactly why the code was having such difficulty changing over to date format, but this is the long way. 
SpeciesAccWinter$Start.Date<-mdy(SpeciesAccWinter$Start.Date)
SpeciesAccWinter$End.Date<-mdy(SpeciesAccWinter$End.Date)
SpeciesAccWinter$td.photo<-as.POSIXct(SpeciesAccWinter$td.photo,format="%Y:%m:%d %H:%M:%S")
SpeciesAccWinter$Photo.Date<-mdy(SpeciesAccWinter$Photo.Date)
SpeciesAccWinter$Photo.Time<-hms(SpeciesAccWinter$Photo.Time)

accumulationWinter<-acc.curve(SpeciesAccWinter, 2020.1)

#Plot the curve!

Winter<-ggplot(accumulationWinter, aes(x=Camera.trap.days, y=species)) +
     geom_line(aes(y=species-sd), colour = "grey50", linetype= "dotted")+
     geom_line(aes(y=species+sd), colour = "grey50", linetype= "dotted")+
     geom_line() + ylab("Number of Species") + xlab("Camera Trap Days") +
     theme_bw()+ geom_hline(yintercept = 12, color = "red")+labs(title = "Winter")+ theme (plot.title =element_text(hjust = 0.5))


ggsave("Species_Accumulation_Winter.JPG", device = "jpg")

```

Species Accumulation for spring season
```{r}
SpeciesAccSpring$Start.Date<-mdy(SpeciesAccSpring$Start.Date)
SpeciesAccSpring$End.Date<-mdy(SpeciesAccSpring$End.Date)
SpeciesAccSpring$td.photo<-as.POSIXct(SpeciesAccSpring$td.photo,format="%Y:%m:%d %H:%M:%S")
SpeciesAccSpring$Photo.Date<-mdy(SpeciesAccSpring$Photo.Date)
SpeciesAccSpring$Photo.Time<-hms(SpeciesAccSpring$Photo.Time)

accumulationSpring<-acc.curve(SpeciesAccSpring, 2020.2)

Spring<-ggplot(accumulationSpring, aes(x=Camera.trap.days, y=species)) +
     geom_line(aes(y=species-sd), colour = "grey50", linetype= "dotted")+
     geom_line(aes(y=species+sd), colour = "grey50", linetype= "dotted")+
     geom_line() + ylab("Number of Species") + xlab("Camera Trap Days") +
     theme_bw()+ geom_hline(yintercept = 14, color = "red")+labs(title = "Spring")+ theme (plot.title =element_text(hjust = 0.5))


ggsave("Species_Accumulation_Spring.JPG", device = "jpg")
```

Species Accumulation for summer season
```{r}
SpeciesAccSummer$Start.Date<-mdy(SpeciesAccSummer$Start.Date)
SpeciesAccSummer$End.Date<-mdy(SpeciesAccSummer$End.Date)
SpeciesAccSummer$td.photo<-as.POSIXct(SpeciesAccSummer$td.photo,format="%Y:%m:%d %H:%M:%S")
SpeciesAccSummer$Photo.Date<-mdy(SpeciesAccSummer$Photo.Date)
SpeciesAccSummer$Photo.Time<-hms(SpeciesAccSummer$Photo.Time)

accumulationSummer<-acc.curve(SpeciesAccSummer, 2020.3)

Summer<- ggplot(accumulationSummer, aes(x=Camera.trap.days, y=species)) +
     geom_line(aes(y=species-sd), colour = "grey50", linetype= "dotted")+
     geom_line(aes(y=species+sd), colour = "grey50", linetype= "dotted")+
     geom_line() + ylab("Number of Species") + xlab("Camera Trap Days") +
     theme_bw()+ geom_hline(yintercept = 14, color = "red")+labs(title = "Summer")+ theme (plot.title =element_text(hjust = 0.5))


ggsave("Species_Accumulation_Summer.JPG", device = "jpg")
```


Species Accumulation for summer season
```{r}
SpeciesAccFall$Start.Date<-mdy(SpeciesAccFall$Start.Date)
SpeciesAccFall$End.Date<-mdy(SpeciesAccFall$End.Date)
SpeciesAccFall$td.photo<-as.POSIXct(SpeciesAccFall$td.photo,format="%Y:%m:%d %H:%M:%S")
SpeciesAccFall$Photo.Date<-mdy(SpeciesAccFall$Photo.Date)
SpeciesAccFall$Photo.Time<-hms(SpeciesAccFall$Photo.Time)

accumulationFall<-acc.curve(SpeciesAccFall, 2020.4)

Fall<- ggplot(accumulationFall, aes(x=Camera.trap.days, y=species)) +
     geom_line(aes(y=species-sd), colour = "grey50", linetype= "dotted")+
     geom_line(aes(y=species+sd), colour = "grey50", linetype= "dotted")+
     geom_line() + ylab("Number of Species") + xlab("Camera Trap Days") +
     theme_bw()+ geom_hline(yintercept = 19, color = "red") +labs(title = "Fall")+ theme (plot.title =element_text(hjust = 0.5))


ggsave("Species_Accumulation_Fall.JPG", device = "jpg")
```


```{r}
library(ggpubr)
Accumulation<-ggarrange(Winter,Spring,Summer,Fall, ncol = 2, nrow = 2,legend = "right", common.legend = TRUE)
Accumulation
ggsave("Species_Accumulation.JPG", device = "jpg")
```

