---
title: "R Notebook"
output: html_notebook
---
Code for stepwise regression in R

Prep the workspace
```{r}
rm(list = ls())
library(MASS)
library(caret)
library(dplyr)
```
Load the draft data
```{r}
KA<-read.csv("Covariates.csv")

#LS<-read.csv("/Users/ebar/Dropbox/1Courses/ResearchGroup/2019-2020/Leslie/SYEvariables.csv")
```
Deal with NA's.

Stepwise regression won't work well if you have different amounts of data for the different regression runs.  Thus, we need a data set with the same data for each regression model. In Kate's data, there are some cameras for which there were no species detected.  We will delete them from the data set.
```{r}
#Species Richness
dump<-which(is.na(KA$SpecRichness))
KA<-KA[-dump,]

#Shannon Diversity
dump<-which(is.na(KA$div_shan))
KA<-KA[-dump,]

#Inverse Simpson's Diversity
dump<-which(is.na(KA$inv_simp))
KA<-KA[-dump,]
```

Isolate response and predictor variables
```{r}
#Species Richness
Kresponse<-KA[, c(7: 8, 18:19)]
Kpreds<- KA[, c(4, 6, 9:17, 21:56)]
Kpreds<- dplyr::select(Kpreds, -starts_with("P_Barren"))
Kpreds<-dplyr:: select(Kpreds, -starts_with("PlotShape"))

#For regression without season 
Kpreds<- dplyr::select(Kpreds, -starts_with("Season"))

#Shannon Diversity
Kresponse<-KA[, c(7: 8, 18:19)]
Kpreds<- KA[, c(4, 6, 9:17, 21:56)]
Kpreds<- dplyr::select(Kpreds, -starts_with("P_Barren"))
Kpreds<-dplyr:: select(Kpreds, -starts_with("PlotShape"))

#For regression without season 
Kpreds<- dplyr::select(Kpreds, -starts_with("Season"))

#Inverse Simpson Diversity
#Shannon Diversity
Kresponse<-KA[, c(7: 8, 18:19)]
Kpreds<- KA[, c(4, 6, 9:17, 21:56)]
Kpreds<- dplyr::select(Kpreds, -starts_with("P_Barren"))
Kpreds<-dplyr:: select(Kpreds, -starts_with("PlotShape"))

#For regression without season 
Kpreds<- dplyr::select(Kpreds, -starts_with("Season"))

```
Now if there are any predictors remaining for which there are NA's, we should remove them from the predictor list. Use dplyr to find them.

```{r}
haveNAs<-Kpreds %>% select_if(function(x) any(is.na(x))) %>% names()
#returns column names that contain NAs
```
Now remove those columns from Kpreds
```{r}
Kpreds<-dplyr::select(Kpreds, - all_of(haveNAs))
```

Now let's run a stepwise regression

Set seed for reproducibility
```{r}
set.seed(123)
```
Using MASS

```{r}
full.model<-glm(Kresponse$SpecRichness ~ ., data = Kpreds)
step.model<-stepAIC(full.model, direction = "both", trace = FALSE)
summary(step.model)

```
Using a second approach to get different outputs using the train() function from caret package.

Another approach following [this website](https://www.statology.org/stepwise-regression-r/)

Start by defining the intercept-only model
```{r}
#Species Richness
m.intercept_only<-glm(Kresponse$SpecRichness ~ 1, data = Kpreds)

#Shannon Diversity
m.intercept_only_Shan<-glm(Kresponse$div_shan ~ 1, data = Kpreds)
```
Define the total model
```{r}
#Species Richness
m.total<-lm(Kresponse$SpecRichness ~ ., data = Kpreds)

#Shannon Diversity
m.total.Shan<-lm(Kresponse$div_shan ~ ., data = Kpreds)
```
Perform stepwise regression
```{r}
#Species Richness
m.stepwise<-step(m.intercept_only, direction = "both", scope = formula(m.total))

#Shannon Diversity
m.stepwise_Shan<-step(m.intercept_only_Shan, direction = "both", scope = formula(m.total.Shan))
```
Now run the final model
```{r}
m.final<-lm(Kresponse$SpecRichness ~ Season + P_Wetland50 + Cam_Orient + Elevation50, data = Kpreds)
summary(m.final)
```
All subsets regression.  See [this webpage](https://educationalresearchtechniques.com/2017/02/24/subset-regression-in-r/)

```{r}
library(leaps)

#Species Richness
m.all_subsets<-regsubsets(Kresponse$SpecRichness ~ ., data = Kpreds)
all_summary<-summary(m.all_subsets)
plot(m.all_subsets, scale = "r2")

#Shannon Divesity
m.all_subsets_Shan<-regsubsets(Kresponse$div_shan ~ ., data = Kpreds)
all_summary<-summary(m.all_subsets_Shan)
plot(m.all_subsets_Shan, scale = "r2")

#Inverse Simpson's Diversity
m.all_subsets_Simp<-regsubsets(Kresponse$inv_simp ~ ., data = Kpreds)
all_summary<-summary(m.all_subsets_Simp)
plot(m.all_subsets_Simp, scale = "r2")
```
Plot some results for model comparison
```{r}
#base plotting
par(mfrow = c(1,2))
plot(all_summary$cp)
plot(m.all_subsets,scale = "Cp")

#Shan_Div
plot(m.all_subsets_Shan,scale = "Cp")

#Inverse Simpson's Diversity
plot(m.all_subsets_Simp,scale = "Cp")
```

Image on left suggests that a model with 3 predictors is best, but doesn't tell which four. Image on the right tells which 3 to select.

```{r}
library(ggplot2)
#Species Richness
plot(m.all_subsets, scale = "Cp")

#Shan_div
plot(m.all_subsets_Shan, scale = "Cp")

#Inverse Simpson's Diversity
plot(m.all_subsets_Simp,scale = "Cp")
```
Shows that spring, winter, and Slope50 are best in model.

And now use bayesian information criterion BIC
```{r}
plot(all_summary$bic)
```

```{r}
#Species Richness
plot(m.all_subsets, scale = "bic")

#Shan_div
plot(m.all_subsets_Shan, scale = "bic")

#Inv_Simp
plot(m.all_subsets_Simp, scale = "bic")
```
BIC indicates a 2 or 3 feature model is best, and chooses season spring, season winter, and Slope50 as best.




```{r}
Test<-lm(Kresponse$inv_simp ~ Season+P_Forest50, data = Kpreds)
summary(Test)
```

